Critical assessment of Linear-Response Excitations in Molecular system\\ or \\ On the Localization of the Linear-Response excitations in Open Systems

### 2017-12-20 LRDraft.tex
update

The Liouville equation \eqref{LiouvillianRho'omegaDef3} can be written in the basis of transititions and becomes a linear matrix equation for the rank-2 vectors
of the coefficients \eqref{OperatorTransitionCoeffDef1} of the operators in its left and right side:
\be
\omega\mat{ \trace{\decay{\alpha}{p}\dm'(\omega)} \\ \trace{\excite{p}{\alpha}\dm'(\omega)}} - 
\mat{ \trace{\decay{\alpha}{p}\Liouv\dm'(\omega)} \\ \trace{\excite{p}{\alpha}\Liouv\dm'(\omega)}} =
\mat{ \trace{\decay{\alpha}{p}\commutator{\op\Phi(\omega)}{\dmnot}} \\ \trace{\excite{p}{\alpha}\commutator{\op\Phi(\omega)}{\dmnot}}}
\;.\nn
\ee
The second addend in the l.h.s can be further analyzed by writing the transition basis expansion of $\dm'$ inside the traces. Performing this procedure
we can recast this quantity as the action of a 2-dimensional matrix on the rank-2 vector of the response density. So we have: 
\be\lb{LiouvilleTransBasisDef1}
\sum_q\sint\dd\beta \left[\omega\delta_q^p\delta(\alpha-\beta)- \optr{L}^{p \alpha}_{q\beta} \right]\sket{q\beta}{\dm'(\omega)} =
\sket{p\alpha}{\commutator{\op\Phi(\omega)}{\dmnot}} \;.
\ee
with:
\be
\optr{L}^{p \alpha}_{q\beta} \equiv \mat{\trace{\decay{\alpha}{p}\, \Liouv\, \excite{q}{\beta}} &
\trace{\decay{\alpha}{p}\, \Liouv\, \decay{\beta}{q}} \\
\trace{\excite{p}{\alpha}\, \Liouv\, \excite{q}{\beta}} &
\trace{\excite{p}{\alpha}\, \Liouv\, \decay{\beta}{q}}} \;.
\ee

>>>>

The Liouville equation \eqref{LiouvillianRho'omegaDef3} can be consistently written in the transition basis. Indeed, its r.h.s is explicitly written
as a commutator with $\dmnot$, while an inspection of the formal definition of the response density and of the Liouville superoperator evidences that
they both contain a commutator with $\dmnot$. Written in the basis of transitions Liouville equation becomes a linear matrix equation for the rank-2 
vectors of the coefficients \eqref{OperatorTransitionCoeffDef1} of the operators in its left and right side:
\be
\omega\mat{ \trace{\decay{\alpha}{p}\dm'(\omega)} \\ \trace{\excite{p}{\alpha}\dm'(\omega)}} - 
\mat{ \trace{\decay{\alpha}{p}\Liouv\dm'(\omega)} \\ \trace{\excite{p}{\alpha}\Liouv\dm'(\omega)}} =
\mat{ \trace{\decay{\alpha}{p}\commutator{\op\Phi(\omega)}{\dmnot}} \\ \trace{\excite{p}{\alpha}\commutator{\op\Phi(\omega)}{\dmnot}}}
\;.\nn
\ee
The second addend in the l.h.s can be further analyzed by writing the transition basis expansion of $\dm'$ inside the traces. Performing this procedure
we can recast this quantity as the action of a 2-dimensional matrix on the rank-2 vector of the response density. So we have: 
\be\lb{LiouvilleTransBasisDef1}
\sum_q\sint\dd\beta \left[\omega\delta_q^p\delta(\alpha-\beta)- \optr{L}^{p \alpha}_{q\beta} \right]\sket{q\beta}{\dm'(\omega)} =
\sket{p\alpha}{\commutator{\op\Phi(\omega)}{\dmnot}} \;.
\ee
with:
\be\lb{LiouvilleMatrixTransBasisDef1}
\optr{L}^{p \alpha}_{q\beta} \equiv \mat{\trace{\decay{\alpha}{p}\, \Liouv\, \excite{q}{\beta}} &
\trace{\decay{\alpha}{p}\, \Liouv\, \decay{\beta}{q}} \\
\trace{\excite{p}{\alpha}\, \Liouv\, \excite{q}{\beta}} &
\trace{\excite{p}{\alpha}\, \Liouv\, \decay{\beta}{q}}} \;.
\ee
This formulation of the Liouville equation is the starting point for the derivation of the spectral decomposition of the response density operator
in terms of the eigenvectors if the Liouville operator. 
The first step in the achievement of this result is provided by the construction of the eigenvectors of the matrix \eqref{LiouvilleMatrixTransBasisDef1}.
Following the notation previously defined we introduce the rank-2 vectors $\sket{p\alpha}{E}$ and $\sbra{p\alpha}{\tilde E}$ that represent, by definition,
the right and left eigenvectors $\optr{L}$, respectively, so that:
\be\lb{LiouvMatrixEigenvectorDef1}
\sum_q \sint \dd \beta \optr{L}^{p \alpha}_{q\beta} \sket{q \beta}{E} = E \sket{p\alpha}{E} \;, \quad
\sum_p \sint \dd \alpha \sbra{p\alpha}{\tilde E} \optr{L}^{p \alpha}_{q\beta} = E \sbra{q\beta}{\tilde E}\;.
\ee
In general, left and right eigenvectors do not coincide, but it is always possible to choose they normalization so that a orthonormality conditions among the
elements of left and right spaces holds, namely:
\be
\sum_p \sint \dd \alpha \sbra{p\alpha}{\tilde E}\sket{p\alpha}{E'} \equiv \dbraket{\tilde E}{E'} = \delta(E-E') \;.
\ee
Once that the eigenvectors are known, the spectral decomposition of the resolvent of $\optr{L}$ can be provided:  
\be
\left[\left(\bbomega-\optr{L}\right)^{-1}\right]^{p\alpha}_{q\beta} =\sint\dd E
\frac{\sket{p\alpha}{E}\sbra{q\beta}{\tilde E}}{\bbomega-E} \;,
\ee
so equation \eqref{LiouvilleTransBasisDef1} can be inverted:
\be
\sket{p\alpha}{\dm'(\omega)} = 
\sint\dd E \sket{p\alpha}{E}
\frac{\sum_q \sint \dd \beta\sbra{q\beta}{\tilde E}
\sket{q\beta}{\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \;,
\ee
that can be compactly rewritten by using the index-less notation:
\be
\sket{p\alpha}{\dm'(\omega)} = 
\sint\dd E \sket{p\alpha}{E}
\frac{\dbraket{\tilde E}{\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \;,
\ee

% \be
% \sket{p\alpha}{E} \equiv \mat{X_E^{p\alpha} \\ Y_E^{p\alpha}}
% \;,
% \quad
% \sbra{p\alpha}{\tilde E} \equiv \mat{\tilde X_{E\,p\alpha} & \tilde Y_{E\,p\alpha}}
% \ee
